### 2016-02-09 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Edits to DelCo FDS validation report

\section{Test Structures}
\label{sec:Test_Structures}
Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}. The structures were designed to simulate a single-story and a two-story residential structure. The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61 m (2 ft). The joints and gaps between the blocks were filled with high temperature insulation.

@@

\subsection{East Structure}
\label{sec:East_descr}

@@

>>>>

\section{Test Structures}
\label{sec:Test_Structures}

\subsection{Construction}
\label{sec:construction}
Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}. The structures were designed to simulate a single-story and a two-story residential structure. The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61 m (2 ft). The joints and gaps between the blocks were filled with high temperature insulation.

@@

@@

\section{Propane Burners}
\label{sec:Burners}
Three propane burners, each with a 0.6 m X 0.6 m square opening 0.14 m above the floor, were used as the fuel source in every experiment described in this report. Propane flowed at a known volumetric flow rate during the experiments.
